\documentclass[Coomer-main.tex]{subfiles}

\begin{document}

\appendix
\addtocentrydefault{part}{}{Appendix}
\chapter{Examples}
\label{ch:app}

A common request across the many versions of this guide has been the inclusion of more concrete examples for the things discussed within. While attempts have been made to do so for most of the sections, in the case of \wi and \rem, including long-form examples is often detrimental to the formatting, pace, and overall flow of the core guide. As such, this appendix of short examples has been provided and referenced in order to display some of the recommended practices in action.

\section{World Info}

The best and most up-to-date examples for World Info that I have at the time of writing are from my scenario “A Summer’s Exchange”\footnote{Check it out \href{https://play.aidungeon.io/main/scenarioView?publicId=c2cf5da0-390d-11eb-ae47-b9ecf242a75d}{here}!}, which deals with three secondary characters that come and go relative to the player character. These are their \wi entries:

\begin{WI}{Arliana, Mrs. Yinris, Arliana Yinris}
Entry: Arliana is the mother of the Yinris household. Arliana is mature by elf standards but still looks quite young and pretty to a human. Arliana is a caring mother for her children and a loving, doting host for her guests. Arliana’s chest is much larger than the average elf. Arliana is very sensitive about the size of her chest.
\end{WI}

\begin{WI}{Vel, Velatha, Velatha Yinris}
Entry: Velatha is the younger of Arliana's daughters. Velatha is a shy bookworm that has trouble coming out of her shell, despite being quite smart. Velatha's ears are unusually long, and they droop slightly, which is something she's very self-conscious of. Velatha's longer ears are more sensitive than elf ears usually are.
\end{WI}

\begin{WI}{Sol, Solana, Solana Yinris}
Solana is the older of Arliana's daughters, the picture of a youthful elven beauty. Solana is gorgeous, and stuck up about it. Solana is excessively snobby and haughty, especially towards other races like humans. Despite being fairly dim-witted herself, Solana is both petulant and impatient. Solana's body has one flaw: she's completely flat, and that's a topic sure to make her furious if brought up.
\end{WI}

As well as \wi entry for their household to keep the family’s relationships to one another consistent:

\begin{WI}{Yinris, Yinris Household, House Yinris, Yinris Family}
The Yinris household includes mother Arliana and her two daughters Solana and Velatha.
\end{WI}

\section{/remember}

There are two distinct kinds of \rem that merit presentation in this body of examples. The first is your usual \rem for a standard piece of erotic writing that has cropped up in a larger adventure. This is entry is also taken from a playthrough of A Summer’s Exchange:

\begin{/rm}
You are Anon, a human exchange student from the University of Magecraft. You know very little about elves, their culture, or their customs. You are often unaware of how badly elves lust after you. You are staying with the Yinris Household, your host family for your cultural exchange trip.

You are currently in Velatha’s bedroom, alone with her after a confession of love.

Velatha is nervous, excited, and teeming with lust after confessing her love to you and dragging you into her bedroom. Velatha is wearing her usual green mage’s robe with her dark brown hair tied back.

The rest of the Yinris family is at home in their own rooms. You and Velatha cannot be caught together, so silence and secrecy is essential.
\end{/rm}

Here you can see each paragraph touching on a part of the recommended order to help bring a scene together, which will also be assisted by Velatha’s character \wi we set up earlier.

The second kind of /remember format is the kind for “Instant Encounters”. That is, a /remember for scenarios that begin with and are exclusively focused on smut, where ALL details are immediately important so that the action can get started accurately, and right away.

The example put forth here is from my scenario “A Bogey’s Prey”, where the AI immediately requires the details of the Bogey monstergirl in order to begin the prompt correctly. So, we push a lengthy chunk of information in violation of the recommended order like this:

\begin{/rm}
You are Anon, a worn-out man filled with numb sadness.

A Bogey is a kind of Oni with big, fluffy arms and legs that are soft like a plush toy stuffed with cotton. Being a sub-species of Oni, Bogeys easily tower over humans with their height, as well as possessing a pair of large horns that sprout from the sides of their head. A Bogey's horns are just as soft and plushy as the rest of their bodies. Bogeys are drawn to men filled with sadness of any kind, and are filled deep, protective instincts. The hands of a Bogey are big, plushy paws nearly the size of their bodies, which Bogeys use to embrace their prey in their big, soft arms. The gentle, warm hug of a Bogey has the power to alleviate any fear, anxiety, or sadness. Once held in the arms of a Bogey, their prey will want to indulge in their affection like a vulnerable child, at which point a Bogey will do everything to soothe and console them, especially with their body.
\end{/rm}

There’s still that line at the top that clearly anchors “You” to your character’s name, as well as that quick bit about how your character is supposed to behave, but the rest of it is entirely dedicated to defining the Bogey in quite a lot of detail. At first glance, many users would raise the concern that this is overstuffing the memory (it clocks in at 941/1000 characters), but when there is no WI for this scenario to crowd additional context, this method actually proves to be quite robust.

The key thing to keep in mind is that the “Instant Encounter” formatting method for your /remember is ONLY for scenarios that absolutely hinge on the smut, and do NOT attempt to introduce more information through World Info. It is absolutely powerful, but the use case is highly specific. For all other cases, stick to the recommended order and assist with supplemental World Info entries. (Just remember you only get about two WI entries alongside a full remember before the AI will start ignoring them due to memory limits)

\section{Author’s Notes}

No special education here, just some examples that you can dissect alongside the guide’s explanations:

\begin{/an}
Elves find themselves overtaken by a slowly-building lust in the presence of a human. Their lusty need to be bred by humans is endemic but well hidden.
\end{/an}

\begin{/an}
Cuddling ahead. Slow and rich erotic details for the smut here. Strong focus on the soft, plushy body of the Bogey and how soothing she is.
\end{/an}

\begin{/an}
This is a story of romance, eroticism, and passion. Slow, rich details for the smut here. Strong focus on the fluffy, warm, soft body of the Bunyip.
\end{/an}

\begin{/an}
Anon is a strong and gentle person who is concerned for the Scylla he has just rescued. Anon is bewildered by the Scylla's appearance.
\end{/an}

\begin{/an}
There is panic and tension to the writing here, mixed with erotic details as the Night Gaunt hunts and lusts after Anon.
\end{/an}

As always, look into the scenarios published by other people that you enjoy and find to be well-functioning. By examining and dissecting the construction of their memory, you can quickly learn quite a lot about how to get what you want out of the AI. This appendix is merely a series of examples from a singular author, following specific guidelines. Do your best to figure out what works through your own experiences, the study of other people’s methods, and a healthy amount of modification. Best of luck!

\end{document}
