\documentclass[Coomer-main.tex]{subfiles}

\begin{document}

\epign{The coomer's greatest muscle is not his dick, but his mind.}
\addchap{Preface}
\label{ch:preface}

\lettr Welcome to—or welcome back—to the Coomer's Guide to \aid.
This is a guide for moderately skilled users of \aid that are looking to increase the quality of their erotic writing through the use of \aid's many powerful features.

The advice and conclusions of this guide can generally be applied to any of \aid's offered models, but a majority of the research conducted for this guide was done with the Dragon model.
The methods put forth in this guide have been cultivated through both my own experiences and research, as well as extensive discussions and review with the \aid community.
The effectiveness of this guide is not guaranteed, and the modification of its rules and recommendations is something I would actively encourage in order to see better results.

As a final but very important note before we begin, this guide is not for beginners, nor is it a guide for general usage.
If you are new to \aid, please refer to Avsfag's /AIDG/ Writing Guide in order to become familiar with the basics.
Likewise, if you are looking for advice on how to conduct a regular adventure with \aid, you will not find it here.
As the title implies, this guide is solely focused on how to bend the mechanics of \aid in order to produce high-quality erotic writing.

With all that said, if you are already familiar with \aid on an intermediate level, and are looking for smut-specific advice, proceed at your leisure.

\chapter{Prompts}
\label{ch:prompts}

Prompts are the bedrock of any \aid adventure that goes beyond the simplistic constraints of Worlds or the Default Prompts.
Prompts are integral to quality erotic writing, because they allow you to create fine-tuned setups for the kind of smut you want without having to coax it out of an unrelated adventure.
However, in order to improve the quality of your erotic writing, you must also learn how to improve the quality of your prompts.

\section{Tenets of a Good Prompt}
\label{sec:tenets}

\subsection{A Summary, Not A Story}

Especially for erotic writing, prompts should not waste characters on lengthy summaries of rich detail that attempt to cover every facet of what you want to accomplish—this is what you should be doing after the prompt has kicked things off.

When crafting a prompt, you must always keep in mind its natural impermanence.
A good prompt provides you (and any other user) with the information they need to create a solid and detailed series of resulting actions that guide the story in an interesting and coherent direction after the prompt itself disappears from the AI's memory.

\subsection{A Springboard, Not An Info Dump}

You should always strive to create a prompt that is as effective as possible in as few characters as possible.
Thankfully, erotic writing rarely demands extensive setup.
As long as the prompt establishes a little bit about the setting, characters that will be important for the next 20 actions, and some narrative details to help the user understand where the prompt is meant to go, you will have a solid prompt.

The idea is to create a prompt that lets you quickly and effectively guide the actions that follow in an appropriate level of detail to continue the story properly.
A prompt should always serve as a springboard for the user's ideas and actions, not an info dump that heaps 2000 characters of lore on them and then leaves them sitting in a lounge chair with no goal.

\section{Think Big, Start Small}

How specific or vague a prompt ultimately is does not matter, as it has no bearing on the tenets outlined above.
All that matters is that you have crafted a prompt that kicks off your story in a way that creates a satisfying series of resulting actions that will carry on the story after the prompt disappears from memory.

With erotic writing in particular, you are often better served with gearing a prompt towards a very streamlined setup that is heavy on situational action and light on narrative background, as opposed to the inverse.
In most cases, extensive narrative setup is wasted on prompts crafted with erotic writing in mind, as the erotic writing itself will quickly consume the AI's ability to focus on much of anything else.

For both erotic and non-erotic prompts, it is recommended that even if your concept for a prompt is very grandiose, you should scale it back so that what you ultimately present to the AI is a slice of what you have in mind.
Any additional information and concepts outside of the springboard discussed in the previous subsection should be relegated to \rem and \wi.
How you go about that is what we will discuss later on in this guide.

\subsection{From Prompt to Story}

Perhaps the most important part of a prompt—especially for erotic writing—is the final section where what you have written is going to be continued by the AI or the user.
This final segment of a prompt and its construction is something you should pay very close attention to if you want your prompt to function correctly.
What the tail end of your prompt can look like is limitless, but what it must include is a very clear path forward for the AI and the user.

Once again, erotic writing prompts hinge on situational action, so in most cases having the end of your prompt act a segue into a specific situation that draws upon the prompt's information is always a safe bet.
What this segue is, and what the resulting situation looks like is once again almost limitless, but it should be one that forces the user to determine their next action with the details and setup of your prompt in mind.

Overwhelmingly, the erotic writing prompts that gain the most widespread appeal are ones that effective outline the start of some encounter, give the user context for what they're doing and who they're getting intimate with, and then clearly pose the path forward for that encounter.

\chapter{The Remember Box}
\label{ch:remember}

The key to ensuring that erotic scenes will flow coherently with the AI—without your constant intervention—is your \rem box.
With 1000 characters to work with as the most front-and-center component of Memory, utilizing it to the fullest for better erotic writing is often a tricky task for even intermediately skilled users.
The recommended usage of \rem is as a repository of immediately important information and details related to your character, their partner, and the current setting of your encounter.

The words ‘immediately important’ are the most critical separator of the \rem box's purpose from World Info.
Whereas World Info should handle more background details and information, \rem is where all the information you need in the present moment to conduct a scene should be placed.

\section{The Recommended Order}

When entering information into your \rem, you should strive to follow a logical order of information, starting from top to bottom:

\begin{itemize}
	
\item Constant information that will always be needed in immediate memory, such as the name and personality of your character.

\item Current information on the setting, specifically detailing where you are and who you are with.

\item Descriptions and details for your partner(s) and any other present characters.

\item Supplemental information, which is anything the AI needs to keep in immediate memory that isn't relevant to any of the categories above.

\end{itemize}

\section{Formatting}

When composing all of this information in your \rem, ensure that you are chunking each category into its own paragraph.
On top of this, you will still need to ensure that every sentence in your \rem can stand on its own when picked out and presented individually.
Some linked ideas are okay within a paragraph, but the more independent each sentence in your \rem is, the better the AI will behave.

As for the exact wording of the \rem box's contents, it is recommended that you put "Your name is X" as the very first thing in your \rem.
After that, describe the player character in second person for the rest of your \rem.

For concrete examples of how to format your remember, see the relevant appendix section. APPENDIX CITATION HERE

\section{Updating}

After you have composed your \rem, the next important step is updating its contents as your story begins to take shape.
Each paragraph will update at a different pace, which is natural.
When you are knee-deep in a quality piece of erotic writing, sometimes your \rem will not change at all until a given scene has concluded and the story progresses.
While more standard stories have a higher rate of \rem turnover, depending on the kind of erotic writing you are doing, the \rem may end up quite static.
All that matters is that your updates keep pace with what immediately important information is changing.

\chapter{\wi}
\label{ch:wi}

\wi entries are often overlooked for the purposes of erotic writing, but their trigger-based nature grants them unique sway over a story.
While \wi does have interesting uses for smut, it is worth noting that in most to all cases, \wi is optional for erotic writing.

\section{Keys and Composition}

\wi entries must always be composed with a utilitarian mindset.
They need to be sharp and descriptive, while also remaining concise.
In general, your entries should be composed as a singular paragraph of short sentences.
Each sentence in a \wi entry should be able to stand on its own and use the key for the entry, much like how \rem sentences need to be able to stand on their own.
For \wi especially, make sure your sentences are short and to the point.

When it comes to keys, they are usually quite self-evident.
Make sure that the keys for a \wi entry encompass all possible, but specific titles that could be used to bring up the contents of said entry.
This is especially important for characters that have multiple different interpretations, shortenings, or prefixes for their names and titles.

For examples of formatted \wi, see the relevant appendix section. APPENDIX CITATION HERE

\section{Frequent Uses}

As we noted in the introduction for this section, while \wi is largely regarded as optional for erotic writing, it still has a few interesting uses that should not be discounted.

\subsection{Characters}

In stories with several prominent characters that each have specific attributes you want to keep track of, building \wi entries for each of them and assigning the keys to their various monikers is nearly essential so that you aren’t constantly juggling and running up against your /remember’s character allotment. \wi entries automate the process of taking character’s details and attributes in and out of memory as they are needed, instead of shouldering the task onto the user and making them update their \rem constantly as figures in a story come and go. (Which also eats away at /remember’s potential for more useful details) In the context of erotic writing, this practice is most often utilized for writing harem stories, or any sort of erotic story that involves several rotating characters.

In general, character entries should seek to establish broad and concrete things about a given character, such as their species (if different species is important for your setting), their height, a very light rundown of their features, and one or two things about their personality.
Anything deeper should be relegated to \rem once they've established themselves as a part of a scene.

\subsection{Species}

If your story is one that involves non-human species, WI is an excellent assistant for defining the traits of any species you want, even ones that the AI doesn't understand at all.
By making the keys the species name(s), and the entry a description of the species' universal attributes—while still following the formatting guidelines above—you can quickly have a very helpful body of information on whatever species it is you're working with in a given scene injected into context just by using the species' name.

When it comes to erotic writing, species entries see some of their most frequent use in smut.
One of \aid's greatest strengths is that you can get frisky with nearly anything, and species entries can often prove one of your greatest assistants in this area.

\subsection{Miscellaneous}

Much like \an, (or any other facet of \aid) what you can do with \wi is only limited to what you can imagine and then condense into under 500 characters.
While character entries and species entries are the two most common uses of \wi for erotic writing, there are many other more obscure uses for \wi that can assist you in crafting complex and interesting smut.

\wi can also be utilized for specially named objects, defined locations, special substances, even defining slang.
As long as it's something you know you're going to need in the AI's memory at some point, but not necessarily all the time, its typically a good candidate for a \wi entry.

As a closing note for this section, sometimes your \wi entries will need to break convention based on the unique demands or challenges of working with specific characters or species, and that's okay.
Adaptation is at the heart of good writing with \aid.
Just keep in mind that if the details you put in a \wi entry don't show up, or show up incorrectly, don't immediately assume it is because you are doing something wrong.
Sometimes the AI just completely ignores entries, other times it will pull details exclusive to them out of nowhere and make them the focus of scene, which is quite thrilling when it does happen.

Don't be dismayed if it takes a while for you to get a good sense for what a robust \wi entry looks like.
Even highly experienced users tweak and improve their \wi all the time.
People often end up paining very deeply over \wi entries, but especially in the area of erotic writing, you shouldn't trouble yourself with such a hangup.

\chapter{\ans}
\label{ch:ans}

When it comes to giving your story a 'primary directive' in terms of what the AI should be putting the most effort into as the current focus, \an is your tool of choice. \an is capable of instantly turning the direction of a story on its head, while supercharging the AI's ability to describe just about anything with a few short sentences.

\an is a premium-only feature at the time of writing, and can be found just beneath the \rem box, with the placeholder text "Style Hint:".

\section{Primary Uses}

The usages of \an are nearly limitless.
For the sake of elaboration however, we can categorize the basic functions of most \ans into four categories, ordered from most common to least common: Prose, Details, Moods, and Premonitions.

Before we continue, it is important to note that these definitions merely apply to singular sentences in the \an. \an has an overall character limit of 150, which means you can include sentences for all four types if you want, as long as you can make them fit.

\subsection{Prose}

\an was originally introduced on the basis of helping guide and enhance the user's prose, which makes it the most well-known and simplistic of Author's Note's capabilities.
A well-tested and simplistic example of an \an for prose is "This is a story with plenty of erotic detail.", which may seem almost laughably obvious, but is surprisingly helpful for the AI.
In general, \ans for prose should be short and to the point while providing clear-cut guidance on how the AI is meant to behave when sculpting its words.

\subsection{Details}

Detail is the simplest \an category.
It is as simple as specifying a person, place, thing, concept, any detail you want, that you want the AI to focus on more frequently.
Sometimes this can cause the AI to over-focus on what you've specified though, so be aware of what you have in your \an if the AI starts to act a little too narrow-minded.

For erotic writing, detail notes are quite useful, as they allow us to guide the AI's focus towards specific things we want out of a scene.
A good example for where you would want to add something to the \an for detail would be if you want the AI to focus on the specific sensations of your partner.
Putting "Strong focus on the soft, warm body of [Your partner]" in the \an will bring about advanced descriptions of the gentle texture and warmth of your partner’s embrace with surprising speed and effectiveness.

\subsection{Moods}

By noting something about the specific mood of a scene in the \an, such as whether it is ‘tense’, ‘passionate’, or ‘romantic’, you can get the AI to reflect that in its output.
When writing smut, Mood notes are best utilized to dictate the disposition of your, your partner, and/or the disposition you share while interacting with one another.
So notes like "[Your Partner] is a sexually aggressive seductress." or "You and [Your Partner] have been dying to explore each other sexually for weeks." are remarkably potent when it comes to the AI coloring how characters will behave with one another during the course of a scene.

\subsection{Premonitions}

Premonitions are the black sheep of the \an categories, being short-lived and somewhat obtuse compared to the other categories.
Stated plainly, a premonition in your \an is something that makes mention of what is going to or about to occur.
Sentences such as "[Your partner] is about to make a bold sexual advance." or "Your next brothel customer will be a Succubus." have a very good chance of coming true when put in your \an.
This hinges on the rest of your Memory and the story itself being in the right place for such a premonition to come true, however.

The overall point of a premonition is usually to let the AI take the initiative on an upcoming action because you want to work with its interpretation of a spontaneous event instead of composing all of it yourself via action guidance.

\section{Keeping Your A/N Dynamic}

Much like how your \rem should be updated as things in your story change, \an should follow a similar principle.
Some parts of an \an won't change all that often—if ever—while other parts will change quite frequently, depending on their purpose.
What's most important is that you don't forget about your \an, as is all too easy. \an works best as something that is frequently updated so that its incredible power is always being utilized to the fullest.

\section{Expanded uses}

As a final word on \an, it is important to keep in mind that what you can do with it is only limited to the sentences and ideas you can fit into 150 characters, and can easily transcend any of the simplistic categories outlined here.
This entire section is merely one interpretation of how to utilize \an.
As long as you're striving to utilize \an as a way to help firmly guide the AI's hand in a given matter, what you input can take nearly any shape.
For erotic writing especially, this limitless potential is something you should use and abuse frequently in order to get the results you want, whether your ideal results are slow burn romance in a cozy cabin, or high-octane monstergirl fight-sex.

\chapter{Style}
\label{ch:style}

While the other sections of this guide have focused on specific functions, this section will be a larger overview of how you should be conducting inputs with the AI.

\section{What You Give Is What You Get}

Above all other guidelines and maxims put forth in this guide, there are none as important as the phrase "What you give is what you get", or as programmers say, "Garbage in, garbage out".
This philosophy is an idea that rules everything you do with \aid, but especially when it comes to your inputs, which are the meat of the \aid experience.

Perhaps the fastest improvement any user of \aid can make regarding the quality of their inputs is to cease utilizing \Do and \say.
Even intermediately skilled users are found still using \Do and \say inputs for their stories, and while using these input modes isn't necessarily incorrect, exclusively using \story is universally recommended for erotic writing.

If you want high-quality smut, you will need to be investing high-quality effort in terms of what you are feeding the AI as inputs. \aid is a text mimicry tool before all else, so short inputs devoid of detail are going to return short outputs devoid of detail.
This is especially important when considering alternative formats for your Memory, as depriving the AI of natural prose in all but your adventure’s action history is going to have a marked effect on the AI’s ability to describe what you have in Memory with a sufficient level of proficiency and detail.

\section{Improvements For Your Prose}

With all of this being said about the need for high-quality inputs, many users end up struggling with how they are supposed to begin elevating their inputs to a level of quality that returns good results from the AI.
Fortunately, many improvements can be made to the inputs you are handing the AI by running what you want to do with your next input through a few simple considerations that we will discuss in the sub-sections that follow.

An important note before we discuss anything else is that while a strong comprehension of grammar rules is important for keeping the AI's average IQ above room temperature, you do not need to spend your time assembling a vast and flowery vocabulary in order to write good smut with \aid.
That comes after you have a good handle on the rest of this process.

\subsection{Intent}

The first and easiest consideration to keep in mind when assembling input is what you're looking to accomplish with the AI though a given action in the midst of a scene.
It is as simple as asking yourself, "What do I intend for the AI to focus on with this input?", and then fusing that into your language.
For instance, if you are taking off your shirt, you might tell the AI just that, "You take off your shirt".
But if you consider what you want to accomplish by taking off your shirt—perhaps revealing your torso—suddenly you have an idea you can attach to the action.
So, your input becomes "You slide your shirt off your body to reveal your torso".

The AI reacts to this sort of built-in initiative quite well, as it natively signals what you want it to focus on next.

\subsection{Pacing}

Pacing is also quite straightforward, but is something that a lot of \aid users let escape them as they are crafting inputs.
Without reinforcing a sense of pacing to the AI, any sort of erotic writing you attempt will easily collapse in less than 10 actions, without fail.
The AI does not hesitate to begin and end encounters incredibly quickly, which is one of the loudest and most common complaints from users attempting to conduct erotic writing with the AI for the first time. Users will begin a scene, the AI will generate a single instance of "I'm gonna...", and like that it's over.

The remedy is quite simple—adding temporal language to your inputs that signals to the AI that things are moving on a slower time line.
The more drawn-out your sentences are, and the more temporal language you include, the better the AI will be at slowing things down and fixating on the juicy details.
To use our shirt example from the previous subsection, you would add pacing by simply adding "slowly" and "teasingly" to the sentence, making it "You slowly slide your shirt off your body to teasingly reveal your torso".
Since both of these words indicate something done carefully and without speed, the AI will pick up on that and spend more time detailing the process.

This consideration is never bulletproof however, and one of your perennial battles as a smut writer with \aid will be fighting the AI's hair trigger for concluding smut in 10 actions or less.
As a general rule of thumb, the more specific details you add to any given action, the slower the pace of the scene is going to be, and vice versa.
The AI’s penchant for mimicry will kick in and keep things on a slower timeline if it’s trying to imitate you specifying how every single article of clothing comes off in fine detail.

\subsection{Guidance}

Guidance is your third consideration, and one of the most important for really digging into that deeper layer of quality smut.
In short, guidance is all about where your actions are going, what they’re trying to lead to next; guidance is the consideration of the future through your inputs.
It's quite similar to the process of considering your intentions with an action, except this time you should be considering what a given input is supposed to be doing in order to set up the next action—whether that next action is coming from you or the AI does not matter.


Bringing back our trusty shirt example once more, we already have a pretty solid input in the form of "You slowly slide your shirt off your body to teasingly reveal your torso".
And while revealing your torso is already what the next action is likely to be about, say we want to specifically focus on revealing our character's abs.
That's your guidance, right there.
Injecting it is as easy as changing the input to "You slowly slide your shirt off your body to teasingly reveal your torso, pulling away the fabric inch by inch to direct attention to your abs".
Through this process, we have easily signalled to the AI where it needs to focus its predictions regarding the next action—which is what guidance is all about.

Just like that, the AI has a lengthy sentence full of slowed-down language and detail, with a clear idea of what to immediately focus on, and then what to focus on next.

\section{Sensations}

Once you have a good grasp on how to frame quality inputs from a functional perspective, you can start laying on the good stuff.
All good erotic writing primarily centers around deep descriptions of sensation, which is exactly what you should be striving to do with each and every one of your inputs.
When crafting any given action, stop to carefully consider how it affects each of the five senses, and how these sensations can be detailed to make your descriptions more potent.

This is the most basic level of additional detail and should be considered first in the process of spicing up your inputs.
Once you have considered how an action looks, sounds, feels, tastes, and smells, you can then move on to the finer details that involve more abstract concepts (which we will discuss in the following subsection).

Do note that a good input only makes use of relevant senses, not all senses.
You should not be detailing the sound your shirt makes when it comes off your body, because that would be an irrelevant detail for simply taking it off.
However, if your shirt was being violently ripped off your body, sound might suddenly be very important to that description.
The process of determining what senses are important for a given scene is heavily influenced by its dynamic.

\subsection{Character Dynamics}

When it comes to defining the dynamic your character has with your partner, begin by considering the sort of emotional flow state that exists between them.
How do you treat them?
How do they treat you?
How does your treatment of one another affect the emotional climate of the scene?
Most importantly, how does that color your actions?
For instance, a gentle make-out session by the fireplace should have a kiss described very differently than a kiss had during a high-octane episode of wrestling intercourse.
It is ultimately the same action—a simple kiss—but since the dynamic between you and your partner is very different in each of these situations (gentle vs high-octane), you are likely to trend towards softer or more abrasive language in order to reinforce that prevailing sense of emotion.
This is how dynamics influence your details.

For the former gentle scene, a good line might be “You gently press your lips up against hers, the warmth of her touch spreading across your face as she leans in to return the gesture”.
For the latter rough scene, “Your mouth latches onto hers as she tries to shove you into a more submissive position, her lips grinding against yours as you struggle to hold your ground”.

As you can see, the dynamic of a scene affects your word choice for describing sensations.
This applies to all five senses, as well as your emotional sense.
For example, some dynamics would call for your partner's scent to be described as ‘sweet‘, while others would call for them to be described as ‘musky’.
Sometimes a hug is a gentle and tender embrace between lovers, other times it’s a crushing and frightening display of sexual aggression.
It all depends on the sort of tone you're looking to set.

\subsection{Pairing Sensations}

Once you understand how to infuse your writing with good sensations that fall in line with the dynamic between you and your partner, and the tone of a scene, you can take the fun to the next level and begin pairing sensations together through the use of similes and metaphors.
You will most often use similes and metaphors for pairing other sensations with the sense of touch.
It is very easy to over-focus on your tactile senses when writing smut, as it is easily the most prominent form of sensory input for intimacy unless another sense is the focus of a fetish.

Thankfully, by pairing other senses with our descriptions of touch, you can quickly break up any sort of monotony and make your writing quite vibrant.
A classic one I like to break out during the foreplay section of a scene is paying close attention to the sounds your partner is making while the two of you are getting frisky.
A simple "She hums softly as her hands run across your shoulders and down your back, carefully assessing the outlines of your skin" goes a very long way for making a scene pop.
To infuse a simile into that input, we can tack on something that works with our dynamic.
In this case, let's say our dynamic is something gentle and romantic, so we'd make the input into "She hums softly as her hands run across your shoulders and down your back, carefully assessing the outlines of your skin as if you were a delicate puppy".
If your dynamic is a bit rougher, you would change that simile to reflect that.

The best part is that there are no limits on what you can pair and elaborate on with sensations.
When describing something less immediately tangible through text, such as scents or sounds, this technique is especially handy.
By mixing together different kinds of prose, you can quickly elevate "She whispers into your ear" to "The sound of her loving whispers mixed with soft moaning and panting against your ear is like being tenderly spoon-fed warm honey".

As long as you're getting different senses to play off each other in interesting and pleasing ways, you're doing it right.
This technique isn't something that requires hours of thought or tons of deep mystic training.
Just ask yourself what sounds like a hot complement to an already hot idea, and you're on your way.
Part of getting better at this whole process is just playing it by ear and figuring out what makes you coom the hardest.

\section{Improving The AI's Prose}

For all the effort you will invest in your inputs through these considerations, it is an unfortunate truth that the AI is not always going to give back the same level of quality you put in.
At times, the AI does not feel like being cooperative with whatever it is that you're trying to construct in a given scene, which can be quite frustrating.
The important thing to learn is that even if the AI is not working with you perfectly, what it gives you as output can be skillfully bent to your will with a little editing.

After your inputs reach a certain level of quality, the AI's output is usually sufficient as a solid series of starter sentences that you can tweak for quality and tone.
Once the AI has given you a few sentences that work well as a starting point for re-configuring, you are entirely free to run them through the considerations we have just discussed and then use \alt (the edit button) to replace the AI’s output with your remodeled sentences.
Once you start doing this, your smut work-flow will reach new heights.
This process of utilizing the AI's output as a starting point for enhancement—and not focusing on what the AI spits out on your first try as the metric for success—is what many users of \aid are talking about when they refer to \aid as a writing assistant.

As you begin to work with the AI and fill the context window with enough quality text to completely saturate it for a given scene, you will often see the quality of the AI's responses spike dramatically.
This is a unique point you can often take advantage of for erotic writing, where all of the AI's present focus is dedicated to a given scene because all of its active memory and context is centered around it.

\subsection{Making /alter Count}

As a quick rule of thumb, you shouldn't be editing everything the AI gives you, not all the time.
If you find yourself having to make comprehensive revisions to nearly every output, you need to work on something else that's harming the quality of your output.
Likewise, if you find yourself restructuring more than roughly 75\% of a given output, you should just save the idea behind it for later and hit redo.

\section{Perspectives}

As a final section under Style, it is worth mentioning the impact that perspectives can have on your erotic writing, both narrative and character perspectives.

\subsection{First, Second and Third Person}

\aid is structured entirely in second person present tense from the start, and all models have fine-tuning that assists them in reinforcing this narrative perspective.
However, GPT-3's underlying corpus is far, far more extensive than the fine-tuning data the developers have provided.
This means that if you phrase everything correctly, \aid is entirely capable of conducting adventures in first person, as well as any type of third person, in past or present tense.

Third person limited past tense is a common alternative narrative perspective adopted by \aid users, which can provide some interesting advantages.
For erotic writing, third person tends to bring out different kinds of detail in your smut, since the AI is drawing from different parts of its core training data, as well as allowing more intuitive focus shifts between characters in a scene.

When it comes to gearing up the AI for a narrative perspective that isn't second person, it's as easy as phrasing all of your inputs and Memory in the desired perspective and tense.
That way, all of the AI's context is in that perspective and tense, and it will begin to mimic that in its outputs.
If you are at all struggling with the random inclusion of second person artifacts, make sure you aren't including any slip-ups in your inputs or memory that the AI can latch onto. (New users often make the mistake of assuming the “3rd Person Only” switch in settings will immediately convert your adventures to third person past tense.
It does not, as this is merely a toggle for multiplayer that changes the word “You” to whatever your character’s name is.)

Be aware that if you are looking to swap to another narrative perspective in order to escape the frequent fun inclusions of the fine-tuning data in your adventures, this is not a solution.
Even in third person you will still encounter Count Grey, Svelks, and Eternals from time to time while attempting to write your smut.

\subsection{Points of View}

As an interesting sub-note on perspectives, one of \aid's most fascinating ‘hidden feature’ is the ability to drop into other character's points of view during a scene, regardless of your current narrative perspective and tense.
With a simple "[Character]'s POV:" as a \story  input, the AI will immediately change gears and work to output the current events of the story from that character's perspective, often complete with their own thoughts and feelings.

This has very potent and obvious uses for erotic writing if you are looking to keep things varied and explore the experience of smut from both sides.
It is worth nothing that smut written from the female perspective is both absurdly detailed and quite available in GPT-3's training data, and is resource many newer writers can easily tap into with a POV command in order to learn more about what good smut can look like (though not all of it is guaranteed to be good).

\chapter{Tips and Tricks}
\label{ch:tips}

With the core of this guide complete, all that is left is to cover a few extra tips and tricks, before moving on to our summary and closing.

\section{Removing Clothing}

All the way up to even intermediate skill levels, users will struggle and scream against the never-ending pair of pants, the shirt that is always being unbuttoned, the pair of underwear that is always being slid off.
While there is unfortunately no bulletproof solution to this perennial problem, strongly noting what clothes are on, and what are off (Using "You and [Partner] are completely naked." if there are no more clothes) in your \rem does quite a lot to help the AI avoid magically manifesting fresh clothing on you in the midst of getting hot and heavy.

\section{Hook Details}

Another thing that less experienced users can sometimes stub their toes on is the AI seemingly getting hung up on strange tangents in the middle of a scene.
This is (usually) not the AI having some spontaneous cranial meltdown, but rather a series of details in the current story context that have too much sway over events.
For example, describing a monstergirl running her nails across your back can quickly segue into being eviscerated if you are not careful.
Utilizing mild aphrodisiacs can easily plunge your character into a coma of some kind, and so on.
The prose that leads to these unfortunate outcomes can be referred to hook details, since the AI gets hooked on them and doesn't let go until you find the action responsible and rephrase it to shift the focus.

Typically all you have to do is look back a few inputs and change the sensations or intent of a given action, which will quickly right the AI's sense of focus.
The key is realizing when a hook detail is screwing up the direction of your writing and then hunting it down.

\section{Special Story Details}

Sometimes, for erotic writing that strays from the usual uber-vanilla template, you want to add some sort of feature or mechanic to the smut that influences the way a scene plays out, such as an aphrodisiac or piece of jewelry that affects its user in different ways.
Getting these often obtuse ideas to work with the AI may seem difficult, but it is often as simple as giving the potion, bracelet, compound, concept, or mechanic its own \wi entry, and then a line or two in your \rem on how it is meant to function.
You can do this for anything as specific as items, or as vague as terminology definitions that flesh out some part of your erotic experience.

Getting the AI to intuitively comprehend whatever it is you are trying to define is usually a game of constructing your definition using concepts the AI already has a good grasp on.
A common example of this is that you can pair nearly any word you can think of with the word "girl", and the AI will be able to roll with it as a fully functional concept, despite having nothing in its training data for whatever fusion waifu you've just cooked up. This extends to any word pairing for any sort of story detail you want.
This can be very useful if you are conducting erotic writing that hinges on more in-depth ideas or fetishes that need additional reinforcement.

\section{Relative Language and Prose}

In many cases for a piece of erotic writing, when composing things for both memory and actions, you will want the AI to keep specific attributes of a character in mind that are absolutely integral to the way they behave, most frequently size.
Reinforcing whether a character is larger or smaller than you is a task many users struggle with, often because they are attempting to do so with objective language (the Oni is seven feet tall/the Fairy is eight inches tall).
Instead of attempting to anchor a concept like size to hard numbers, which the AI cares nothing for, you should instead use relative language and prose for these concepts.

By stating in your memory that the Fairy is significantly smaller than your character, and then describing her using prose that befits a small flying animal like a bird, instead of a human, you will quickly see the AI become much more aware of the Fairy’s size.
This works just as well in the inverse, describing the Oni as much taller than your character, and using descriptions that hammer home her larger size and stature as well as the more powerful nature of her movements.

\chapter{Summary}
\label{ch:summary}

This guide covers quite a lot of information at varying levels of depth, which naturally mandates a more succinct summary of each section's core takeaways.
This bulleted summary is not a substitute for the actual knowledge of the guide, but more like a useful review of everything you have learned after reading it over.

\begin{enumerate}

\item \nameref{ch:prompts}

\begin{itemize}
\item Prompts are integral to quality erotic writing because they allow you to precisely dictate how your smut starts and what it is about
\item A quality prompt translates to quality erotic writing
\item Good prompts provide the necessary information for a strong start, not excessive lore
\item Good prompts allow the user to quickly and effectively continue the story, well past when the prompt itself fades from active memory
\item For big ideas, make your prompt present a small slice of it to get things started
\item Make sure the transition from prompt to story is as intuitive as possible
\end{itemize}

\item \nameref{ch:remember}

\begin{itemize}
\item The \rem box is for important information that is required for a scene to flow correctly without constant correction
\item Your \rem needs to follow a logical formatting order to keep related ideas together and different concepts separate
\item The individual sentences of your \rem should always strive to stand on their own
\item Your \rem should be updated as a scene evolves and the current focus of the story changes
\end{itemize}

\item \nameref{ch:wi}

\begin{itemize}
\item \wi, while largely optional for erotic writing, can still be useful for certain situations thanks to its trigger\item based nature
\item World Info entries should be utilitarian: descriptive, yet concise
\item \wi keys need to cover enough phrases to accurately load when their contents are mentioned, but not cover so many phrases that an entry loads at an inappropriate time
\item \wi entries can be used to keep track of characters, species, locations, items, and nearly anything that is brought up on a contextual and recurring basis
\end{itemize}

\item \nameref{ch:ans}

\begin{itemize}
\item Second only to your actual inputs, \an is the most active 'guiding hand' in terms of where the AI's current focus and effort is going to be for a scene
\item \an can be used to influence the AI's prose, accentuate specific details, define a scene's mood, and loosely guide future events
\item Your \an should be updated as the various components it addresses evolve with the scene/story
\item The only limit on what you can do with \an is what you can make fit inside 150 characters
\end{itemize}

\item \nameref{ch:style}

\begin{itemize}
\item When it comes to writing anything with the AI, what you give is what you get in terms of quality
\item \story is universally recommended over the usage of \do and \say for any method of input
\item Less natural prose in your memory means less natural prose in your outputs
\item You need to focus on improving your grasp on grammar and story conventions before you try and expand your vocabulary
\item What you intend to accomplish by composing an input should be self\item evident within the input
\item High levels of detail and some temporal language is key to slowing down the AI's pacing of the action
\item You should always make sure your inputs give the AI specific guidance on where it should focus for generating its response
\item All good erotic writing centers around deep descriptions of sensation
\item Consider all senses for an action, then choose the relevant ones
\item How you and your partner behave with one another is your character dynamic, which directly affects the tone and prose of a scene
\item You can pair sensation descriptions together for added variety in your writing
\item The AI will eventually reach a point of context saturation that will make your outputs very well\item focused on a given scene
\item Do not waste your time editing every output, or more than 75% of a single output
\item You can write with the AI in any narrative perspective and tense you want by changing your inputs and memory to the desired type
\item Commands allow you to change the POV for the story between different characters in order to explore their thoughts and experiences
\end{itemize}

\item \nameref{ch:tips}

\begin{itemize}
\item Using your \rem to keep strong track of what clothes are on what characters is key to making sure they come off and stay off
\item Sometimes the AI gets stuck on specific details that will need to be eliminated in order to stop unhelpful tangents in output
\item You can describe specific details and strange concepts to the AI by pairing together concepts it already has a good grasp on
\item Using relative language to describe attributes such as size will give the AI a much better understanding of how to handle a character's actions and descriptions
\end{itemize}

\end{enumerate}

\chapter{Closing}

\lettr A little over 7000 words later, and the core of the guide is complete.
With luck, you have learned a great deal about crafting more complex erotic writing with the AI.
Just remember that change is not instant, results will not materialize before your eyes after a single once-over with this guide.
What you have learned here takes time and effort to get right, like any other skill or hobby.
Your next few attempts won't be perfect—no attempt ever is—and that's okay.

\aid has always been, and always will be about adaptation and experimentation in order to yield better results.
It is inevitable that as you grow and become stronger with erotic writing, the way you interpret, apply, and modify this guide's advice will change as well.
You might struggle at times, especially against the AI, but that's a part of getting better.
Don't hesitate to take a step back every once in a while to clear your head and give your process some room to breathe for a bit.
Now get out there and have fun!
Live like no one else can, and coom mightily.

Big thanks to the anons of /aidg/ and the wider \aid community for their feedback and support across the many iterations of this guide, and for constantly inspiring me to do better.
Specific thanks to PDFanon for all of his hard work on making this wall of text look sexy, to Paragon for all of his proofreading and feedback work on getting this guide to make sense, to Worble for giving the community guides a home on this website of his, and to the anon with Artbreeder that made the guide’s fantastic cover\footnote{\href{https://arch.b4k.co/vg/thread/313360917/\#q313434592}{Link} to the post in question.}.
You're all wonderful.
And, if you've made it this far, having read every single part of this guide (possibly for the fourth/billionth time), thank you.
I hope you enjoyed my guide, and I hope to see you again soon!
\bigskip

(If you have questions or feedback on this guide, or would simply like to get in touch, I am available on Discord\footnote{\href{https://discordapp.com/users/773014944718389248}{Manwhore\#5487}}, as well as by email\footnote{\href{mailto:ManwhoreAnon@gmail.com}{ManwhoreAnon@gmail.com}}.)

\end{document}
